### 2019-02-08 symmetry_properties.tex
ssr

>>>>

\subsection{Number of Strongly Asymmetric NCFs}
\label{sse:number_strongly_asymmetric}

\begin{theorem}\label{thm:count_strongly_asymmetric}
For any $n \geq 2$, the number of Boolean functions with $n$ variables 
that are both strongly asymmetric and NCFs is $n! \, 2^n$.
\end{theorem}

\noindent
\textbf{Proof:}~
Consider a default normalized representation of a strongly asymmetric NCF $f$.
The representation contains $n-1$ layers.
The first $n-2$ layers each contain one line, and the last layer contains two lines.

Consider the canalyzed values in $f$. The canalyzed value in the
first layer can be either 0 or 1.  The canalyzed value in every
other layer is the complement of the canalyzed value in the preceding
layer.  Thus, there are 2 possibilities for the sequence of canalyzed
values in $f$.

The canalyzing variable in each of the first $n-2$ lines (one per
layer) can be any variable that has not yet occurred in a preceding
line.  The last layer contains the remaining two variables.  Thus,
there are $n! / 2$ possibilities for the pattern of variable
occurrences in $f$.

For each of the $n$ variables, the canalyzing value for the line
containing that variable can be either 0 or 1.  Thus, there are
$2^n$ possibilities for canalyzing values.  \QED
